Title

### 2014-07-24 paper.tex
added cross validation result and outline for discussion

% validation
To validate our model, 10-fold cross validation is performed.
The values of precision, recall, F$_1$ score, and accuracy are recorded and then averaged
to give the overall performance of our model.

@@

@@

As expected, most comments classified as \emph{negative} have score of 0 and 1,
while most \emph{positive} comments have score of 2 and 3.
However, some comments in every score were lost and classified as \emph{neither}.

@@

@@

% stuff

>>>>

% validation
To validate our model, we randomly split the data into 10 parts.
9 parts are used for training, and 1 part for validation.
This process is repeated 300 times. % while I sleep
The values of precision, recall, F$_1$ score, and accuracy are recorded and then averaged
to give the overall performance of our model.

@@

\subsection{Model Generation}

@@

As expected, most comments classified as \emph{negative} have score of 0 and 1,
while most \emph{positive} comments have score of 2 and 3.
However, some comments in every score type were classified as \emph{neither}.

@@

\subsection{Cross Validation}

After we performed cross validation, we obtained the following result:
for positive and negative classifications,
we obtained an average F$_1$ score of 0.693 and 0.681,
with standard deviation of 0.090 and 0.118, respectively.

@@

% noisy data, and binary classification

% tuning the F score for precision and recall

% reasons for classification as useful or not useful

% example of false positive and false negatives
